Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-18 ms.tex
use bold without any arrows or underlining to denote vector quantities

\begin{equation}
\label{eqn:post}
P(\tilde{I}_{545}, T_2|\vec{\mathbf{I}}~) \propto \mathcal{L}(\vec{\mathbf{I}}~|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
\end{equation}

@@

Here $\vec{\mathbf{I}}$ denotes the vector of observed thermal dust intensities quoted 
under the `IRAS convention': $\vec{\mathbf{I}}$ = ($I_{217}$, $I_{353}$, $I_{545}$, 
$I_{857}$, $I_{3000}$). The likelihood function is given by:

@@

\begin{equation} \label{equ:like}
\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \textrm{exp}\Big[-\frac{1}{2}(\vec{\mathbf{I}}-\underline{\mathbf{\tilde{I}}})\Sigma^{-1}(\vec{\mathbf{I}}-\underline{\mathbf{\tilde{I}}})^T\Big]
\end{equation}

@@

Here $\underline{\mathbf{\tilde{I}}}$ is the vector of predicted observations 
based on Equation \ref{eqn:inten} and the proposed values of $\tilde{I}_{545}$ 
and $T_2$: $\underline{\mathbf{\tilde{I}}} = $($\tilde{I}_{217}$, 
$\tilde{I}_{353}$, $\tilde{I}_{545}$, $\tilde{I}_{857}$, $\tilde{I}_{3000}$). 
$\Sigma$ is the covariance matrix constructed based on the uncertainties in the
observed intensities:

@@

\begin{equation}
\label{eqn:f1post}
P(\tilde{I}_{545}, T_2, f_1|\vec{I}~) \propto \mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
\end{equation}

The likelihood here is conceptually the same as that of Equation 
\ref{equ:like}, but now depends on $f_1$, which can vary from proposal to 
proposal within each individual pixel. The other difference is that 
$\vec{\mathbf{I}}$ and $\underline{\mathbf{\tilde{I}}}$ now include 100 GHz, 
143 GHz, 140$\mu$m and 240$\mu$m, in addition to the five bands used for the 
full-resolution fits.

>>>>

\begin{equation}
\label{eqn:post}
P(\tilde{I}_{545}, T_2|\mathbf{I}) \propto \mathcal{L}(\mathbf{I}|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
\end{equation}

@@

Here $\mathbf{I}$ denotes the vector of observed thermal dust intensities 
quoted under the `IRAS convention': $\mathbf{I}$ = ($I_{217}$, $I_{353}$,
$I_{545}$, $I_{857}$, $I_{3000}$). The likelihood function is given by:

@@

\begin{equation} \label{equ:like}
\mathcal{L}(\mathbf{I}|\tilde{I}_{545}, T_2) = \textrm{exp}\Big[-\frac{1}{2}(\mathbf{I}-\mathbf{\tilde{I}})\Sigma^{-1}(\mathbf{I}-\mathbf{\tilde{I}})^T\Big]
\end{equation}

@@

Here $\mathbf{\tilde{I}}$ is the vector of predicted observations 
based on Equation \ref{eqn:inten} and the proposed values of $\tilde{I}_{545}$ 
and $T_2$: $\mathbf{\tilde{I}} = $($\tilde{I}_{217}$, 
$\tilde{I}_{353}$, $\tilde{I}_{545}$, $\tilde{I}_{857}$, $\tilde{I}_{3000}$). 
$\Sigma$ is the covariance matrix constructed based on the uncertainties in the
observed intensities:

@@

\begin{equation}
\label{eqn:f1post}
P(\tilde{I}_{545}, T_2, f_1|\mathbf{I}) \propto \mathcal{L}(\mathbf{I}|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
\end{equation}

The likelihood here is conceptually the same as that of Equation 
\ref{equ:like}, but now depends on $f_1$, which can vary from proposal to 
proposal within each individual pixel. The other difference is that 
$\mathbf{I}$ and $\mathbf{\tilde{I}}$ now include 100 GHz, 
143 GHz, 140$\mu$m and 240$\mu$m, in addition to the five bands used for the 
full-resolution fits.
